RAS2012: Competition Entry

### 2012-06-23 ras2012-paper/src/main/latex/paper/paper.tex
Update the resolved systems.

@@

In this section, we show the best solutions reached for each data set. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 1 GB of heap space inside Java 7 runtime environment. The specific solver configurations used to reach these solutions may not have been the same every time.

Please note that via the benchmarking functionality of Drools planner (see above), users may be able to fine-tune the algorithm. This fine-tuning can be focused either on providing better solutions or on faster turnaround times.

\include{RDS1.txt-1582}.

\include{RDS2.txt-8948}.

\include{RDS3.txt-11697}.

\include{TOY.txt-808}.

>>>>

\section{Achieved results}

Running the algorithm described above 20 times over each data set, we have compiled a set of results, see Table \ref{table:result}. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 2 GB of heap space inside Java 7 runtime environment.

\include{stats}

\begin{figure}
\centering
\includegraphics[width=120mm]{chart.png}
\caption{Plotting the data for the various resolved systems.}
\end{figure}

Please note that via the benchmarking functionality of Drools Planner, users may be able to fine-tune the algorithm to be focused either on providing better solutions or on faster turnaround times. Drools Planner even allows for retrieving the intermediate results of the algorithm and also modify the problem while it's being solved, which makes it the ideal tool for real-time planning.

For statistics of the resolved systems, see tables \ref{table:TOY-808.tex}, \ref{table:RDS1-996.tex}, \ref{table:RDS2-7597.tex} and \ref{table:RDS3-11023.tex} respectively.

@@

In this section, we show the best solutions reached for each data set.

\include{TOY-808}
\include{RDS1-996}
\include{RDS2-7597}
\include{RDS3-11023}
